---
title: "Experimental design"
author: "Meng Le Zhang and Lydia Warden"
date: "22/07/2021"
output: html_document
---

``` {r setup, include = FALSE}

library(tidyverse)
library(tmap)
library(sf)

##  Hotfix latest sf has issues with tmap -- use this fix
## see:  https://github.com/mtennekes/tmap/issues/571
##  and solution to disable S2: https://github.com/mtennekes/tmap/issues/577

sf::sf_use_s2(FALSE)

pairMapList <- readRDS('cleaned data/Quartile maps saved.rds')

tmap_mode('view')
```

# Introduction

A small number of studies use computer algorithms and areal level demographic data to detect community borders. One such study by Dean et al. uses a statistical model to detect sharp community boundaries, referred to as social frontiers. However, to date, none of these studies has validated the accuracy of their algorithms externally using human participants or other means. In this paper, we develop an experimental design that tests whether residents in an area recognise the sharp boundaries produced by the Dean et al. algorithm.

The experiment is a part of a series of semi-structured qualitative interviews with residents. For the qualitative interview, MZ gave the interview team a map of social frontiers in a city produced earlier in the research project. The team chose an area within each city with an above-average number of social frontiers and began sampling participants local to that area (or were connected to it). The primary goal of the sampling method was to maximise the quality of the qualitative data. This place some limitations on the experimental design.



# Experimental design

Fundamentally, we wish to test if social frontiers produced by the Dean et al. routine are more plausible than those produced by an alternative algorithm such as sampling borders at random. Since the interview team chose the area selected for the qualitative interviews based on having social frontiers, a simple random selection of borders will contain many sharp borders by chance. Furthermore, the interview team has already seen a map of social frontiers, which will affect the possibility of having a double-blind.

To address these issues, we propose a design where participants choose between maps with a set of borders with different degrees of sharpness. We subtly alter the borders for each map to i) make it difficult for the interview team to detect the 'correct' map and ii) allow us to make additional inferences.

For borders in the target area, we calculate a measure of sharpness based on the absolute difference in the proportion of foreign-born in LSOAs on each side of the border (the true measure is more complicated, see Dean et al. 20xx). We then standardise this measure and denote it as $\Phi$ where large values indicate sharper boundaries. $\Phi$ is the basis of Dean et al.'s algorithm: any border with a value of $\Phi > 1.96$ was considered substantial and likely to be a social frontier.

Then we group borders into quartiles, where quartile 1 $Q1$ are the sharpest and $Q4$ the least sharp. We then produce maps that include borders from 2 quartile groups. For example, map $Q(1, 3)$ shows borders in quartiles 1 and 3.

We test the following pairs of maps against each other:
- $Q(1, 2)$ versus $Q(3, 4)$ (pair 1)
- $Q(1, 2)$ versus $Q(2, 3)$ (pair 2)
- $Q(2, 4)$ versus $Q(3, 4)$ (pair 3)
- $Q(1, 3)$ versus $Q(2, 3)$ (pair 4)


For each pair, we measure the proportion of participants who prefer the map with the sharpest borders (i.e. the first mentioned map in each pair above, $Q(1, 2)$ in pair 1).
We wil refer this proportion as $P_j$ where $j$ denotes map pairing. The null hypothesis is that the chance of choosing any map is 50%:

$$P_{j=1} = P_{j=2} = P_{j=3} = P_{j=3} = 0.50$$

We also explore whether participants recognise specific border sets as social frontiers regardless of $\Phi$.

## Rationale

Pair 1 tests the sharpest borders in the map against the least sharp borders. Since the difference between the maps are so stark, this comparison yield the largest value of $P_j$ and thus the highest chance of rejecting the null hypothesis. However, the interviewer is likely to recognise map $Q(1, 2). Furthermore, this trial alone cannot tell us the perceived sharpness of borders in each quartile group.

For instance, participants might prefer $Q(1, 2)$ over $Q(3, 4)$ because they perceive the set of borders in $Q2$ to be social frontiers while being ambivalent about $Q1-3$. It is also likely that given so much information, participants rely on heuristics and look for one or two known community borders. These borders may occur in $Q2$ rather than $Q1$.

In either circumstance, we would like to know if participants prefer the borders in $Q1$ versus $Q2$, henceforth written as $Q1 >Q2$. To test the full range of comparisons $Q1 vs Q2$, $Q1 vs Q3$ etc., would require six trials. However, we can limit our comparisons by first assuming:

> if participants prefer $Q1 > Q3$ then they would prefer map $Q(1,2) > Q(2,3)$.

This is because the only difference between the maps is the inclusion of borders in $Q1$ and $Q3$. As such:

- if $Q(1, 2) > Q(2, 3)$ then $Q1 > Q3$ (pair 2)
- if $Q(2, 4) > Q(3, 4)$ then $Q2 > Q3$ (pair 3)
- if $Q(1, 3) > Q(2, 3)$ then $Q1 > Q2$ (pair 4)

To save time, we are uninterested in the relationship between $Q4$ and borders in the other quartiles.


# Map example
**Note** Map order is not randomised in this experiment and proportion of foreign born base layer is not included for participants. Participants will be shown one pair at a time in a random order.

## Pair 1

```{r pair-1, echo = F}
pairMapList[[1]]

```

## Pair 2

```{r pair-2, echo = F}
pairMapList[[2]]

```

## Pair 3

```{r pair-3, echo = F}
pairMapList[[3]]

```

## Pair 4

```{r pair-4, echo = F}
pairMapList[[4]]

```